%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://ax920.github.io/}{\Large Alvin Xu}} & Email : \href{mailto:alvin.xu@alumni.ubc.ca}{alvin.xu@alumni.ubc.ca}\\
  \href{https://ax920.github.io/}{https://ax920.github.io/} & Mobile : (587)223-9978 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of British Columbia}{Vancouver, BC}
      {Bachelor of Science in Computer Science; Minor in Commerce}{Sept. 2018 -- Current}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {AnalysisWorks}{Vancouver, BC}
      {Web Development Intern}{May 2020 - Aug 2020}
      \resumeItemListStart
        \resumeItem{C3.js}
          {C3.js is a D3-based charting library. Worked with the source code to achieve customized tooltip logic. Utilized in several modules to display different healthcare metrics for hospitals in Canada.}
        \resumeItem{Code Refactor}
          {Refactored tables and charts throughout several modules into their own components for increased efficiency and readability.}
        \resumeItem{Error Logging}
          {Wrote a NestJs error logging service to catch thrown errors, unhandled promise rejections and uncaught exceptions on a production application.}
        \resumeItem{UI Mockup}
          {Prototyped several design options for user actions such as active, suspend, deactivate, and reset password, using Invision.}
        \resumeItem{Client Meetings}
          {Participated in meetings with stakeholders and clients to discuss feedback changes and improvements for the web application.}
        \resumeItem{Deploy to Azure}
          {Deployed application to staging and production environments hosted on Azure.}
      \resumeItemListEnd
      
% --------Multiple Positions Heading------------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-----------------------------------------------

    \resumeSubheading
      {UBC Arts ISIT}{Vancouver, BC}
      {IT Helpdesk Support}{Sept 2019 - Dec 2019}
      \resumeItemListStart
        \resumeItem{Customer Service}
          {Provided excellent customer service in a high-traffic environment.}
        \resumeItem{Intepersonal skills}
          {Developed strong interpersonal skills and received positive customer feedback from customers}
        \resumeItem{Adaptability}
         {Demonstrated adaptability by taking direction and constructive advice from managers and co-workers}
      \resumeItemListEnd
    \resumeSubheading
      {AnalysisWorks}{Vancouver, BC}
      {Web Development Intern}{May 2019 - Aug 2019}
      \resumeItemListStart
        \resumeItem{Login}
          {Created a single sign-on login system from scratch with Okta’s OAuth 2.0 and OpenID Connect APIs.}
        \resumeItem{REST}
          {Developed a proprietary RESTful API to connect multiple web applications and maintain a central authentication system.}
        \resumeItem{Git}
          {Coordinated with team members to develop with a feature/master branch workflow in Git.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{ProShop Inventory}
      {Inventory tracking application in use by GYMVMT Edgemont to track the squash proshop's inventory, sales, and profits. \textbf{Angular Express Heroku}}
    \resumeSubItem{VibeIt}
      {Playlist generator that generates curated playlists based on a particular mood (high-energy, studying). \\ \textbf{React Spotify web-api}}
    \resumeSubItem{TypeMeNot}
      {Chrome web extension that warns the user of potentially toxic or offensive language when typing comments on websites such as Reddit, Facebook, Twitter. \textbf{Chrome Extension Google Sentiment Analysis API}}
    \resumeSubItem{Emissions Depot Analysis}
      {Script used by EmissionsDepot that takes a csv file generated from QuickBooks and outputs a sorted list of items based on profit margin. \textbf{Python}}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Languages}{: Typescript, Javascript, Java, C++, SQL, Python}
    }
    \item{
      \textbf{Technologies}{: Angular, React, NestJs, Redux, RxJs, Heroku, Git, Okta}
    }
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
